\documentclass[margin,line]{resume}
\begin{document}
\name{\Large Michael A Wheeler}
\begin{resume}

    % Contact Information
    \section{\mysidestyle Contact\\Information}\vspace{2mm}

    \begin{tabular}{@{} l @{\hspace{38mm}} r}
   16 Erin Cl                &           \\
    Gladstone          &  +61 4 3966 8012\\
    QLD 4680, Australia & employment@michael-wheeler.org\\
    \end{tabular}


    % Research Interests
    \section{\mysidestyle Interests}

    Communications and Networks, TCP IP (v4/v6), Efficient Packet Routing, Security analysis, Radio Communications


    % Education
    \section{\mysidestyle Education}

    {\bf Tannum Sands State High School}, Tannum Sands, QLD , Australia \vspace{2mm}%
    \begin{list1}
    \item[] Grade 12 Studies
    \vspace*{2mm}
    \item[] English, Mathematics B, Physics, IPT, Graphics, 2008
    \end{list1}
    
    {\bf Business, Information Technology Skills Centre  }, Boyne Island, QLD , Australia \vspace{2mm}%
    \begin{list1}
    \item[]  Network Administration
    \vspace*{2mm}
    \item[]  Certificate I in Informations Technology , 2007; Certificate III in Information Technology , 2008
    \end{list1}

    {\bf Cisco Certificates}%
    \begin{list1}
    \vspace*{2mm}
    \item[]  Cisco Certified Network Associate
    \item[]  Cisco CCNP ROUTE
    \end{list1}

     \section{\mysidestyle Currently\\Studying}   
%    {\bf Central Queensland University}, Rockhampton, QLD , Australia \vspace{2mm}%    
     {\bf Self Study}\vspace{2mm}%
    \begin{list1}
    \item[] Cisco Certified Network Professional
    \end{list1}
    % Awards
    \section{\mysidestyle Awards and Certificates} 

2009 Course in General Safety Induction (Construction Industry) Blue Card, 2008 Certificate of Academic Excellence in Information Technology, 2006 
Certificate of Academic Excellence in Information Technology , 2006 Excellence Award - Information Technology , 2006 Excellence Award - Mathematics 
x3 , 2006 Excellence Award - Music , 2006 Excellence Award - Business , 2006 Tour de Chaplain Participation , 2006 Human Powered Vehicle , 2005 The 
University of NSW Australasian Schools Computer Skills Competition - High Distinction , 2005 Mathematics Competition for the Westpac Awards - 
Distinction , 2004 The University of NSW Australasian Schools Computer Skills Competition - High Distinction , 2003 The University of NSW 
Australasian Schools Computer Skills Competition - Distinction , 2003 The University of NSW Australasian Schools Mathematics Assessment - 
Distinction , 2002 The University of NSW Australasian Schools Computer Skills Competition - High Distinction , Comalco Creative Communications 
Award For Green And Health School Competition - Created web site under guidance of Kit Herbert 


  

    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    {\bf Data \#3}, Boyne Smelters Limited \vspace{2mm}\\\vspace{1mm}%
    {\sl Network Administrator} \hfill {\bf April 2012 -- Present}\\
    Details of Position:-
    \begin{list2}
        \vspace*{1mm}
\item Plan, price and deliver projects in a timely fashion
\item Create documentation and procedures for tasks and processes
\item Manage, report and resolve any network related issues or outages
\item Resolve any service desk calls, issues of requests for information in a timely manner within defined SLA
\item Equipment monitoring and analysis of logs and reports
\item Communicate to site any planned or unplanned outages
\item Upgrade core infrastructure to increase reliability of site communications
\item Improve site network security by auditing the network and making changes where available
\item Perform root cause analysis on network issues and implement fixes to prevent recurrence
\end{list2}

    {\bf Data \#3}, Boyne Smelters Limited / Yarwun Alumina Refinery, Rio Tinto IS and T Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Communications Engineer} \hfill {\bf January 2011 -- March 2012}\\
    Details of Position:-
    \begin{list2}
        \vspace*{1mm}
        \item  Upgrade and maintain network infrastructure at Boyne Smelters Limited and Yarwun. This includes installing, upgrading and configuring Cisco switches and routers for use in production environments
\item  Continued use of fault finding skills to solve communication issues
\item  Update databases with new switch information
\item  Improve site network security by auditing the network and making changes where available
\item  Upgrade network infrastructure and software to ensure reliability
\item  Perform root cause analysis on network issues and implement fixes to prevent recurrence
\item  Take part in site upgrade projects for increase capacity
\item  Log job tickets through HP OpenView Service Desk
\item  Monitor networks through Cisco Works
\item  Maintain Cisco Works, Cisco ACS, Cisco WCS infrastructure
    \end{list2}


    {\bf Ergon Energy}, Nexium Telecommunications / Ergon Energy  \vspace{2mm}\\\vspace{1mm}%
        {\sl Telecommunications Specialist} \hfill {\bf November, 2010 -- January 2011}\\
             Details of Position:-
                  \begin{list2}
                          \vspace*{1mm}
                          \item Achieve required customer SLAs for communications service availability, continuity and performance for all customers through carrier class communications services management.
                          \item Undertake network analysis, design, testing and deployment activities for new services so that they are seamlessly 
implemented and managed in order to ensure that network security is maintained to documented standards at all times.
                          \item Provide pre-sales support where required, including service detail design and equipment costing.
                          \item Maintain configuration and support of the operational support systems by providing administration support.
                          \item Provide detailed costing's for projects, along with detailed design diagrams.
			  \item Log tickets through VQSM
			  \item Maintain ITNM, Cisco Works, SNMPc, ACS, and IBM ITNM software
			  \item Monitor the network through SNMPc, Netcool CIC, IBM Tivoli and Solarwinds
                          \end{list2}

    {\bf Hays Recruitment}, Nexium Telecommunications / Ergon Energy  \vspace{2mm}\\\vspace{1mm}%
        {\sl Network Systems Technician} \hfill {\bf February, 2010 -- November, 2010}\\   
             Details of Position:-
                  \begin{list2}
                          \vspace*{1mm}
                          \item Monitor and perform maintenance to network equipment.
                          \item Respond to faults and calls.
                          \item Prepare and apply service configuration.
                          \item Configure networking equipment for field deployment.
                          \item Provide detailed costing's for projects, along with detailed design diagrams.
                          \item Liaise with external teams to ensure effective and on time service delivery, along with fault management. 
                          \item Lodge warranty, and RMA on faulty devices for repair.
                          \item Plan maintenance and system upgrades.
                          \item Log incidents and contact customers with updates.
                          \item Monitor the security of the network and physical infrastructure for intrusions.
                          \item Update documentation and procedures. 
                          \item Ensure backups and automated jobs completed successfully.
                          \end{list2}
    {\bf Data \#3}, Boyne Smelters Limited / Yarwun Alumina Refinery, Rio Tinto IS and T Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Communications Project Engineer} \hfill {\bf November, 2008 -- February 2010}\\
    Details of Position:-
    \begin{list2}
        \vspace*{1mm}
        \item  Upgrade and maintain network infrastructure at Boyne Smelters Limited. This includes installing, upgrading and configuring Cisco switches and routers for use in production environments. 
\item  Update databases with new switch information. 
\item  Setting up Microsoft Windows Servers.
\item  Setup and diagnose Microsoft Windows workstations. 
\item  Solve critical network and wireless control systems issues. 
\item  Operate Symantec Ghost and Microsoft RIS. 
\item  Arrange contractors for cable runs and expansion projects. 
\item  Plan, manage and cost projects for network upgrades in process control and general office areas. 
\item  Ensure security for process control devices and standard workstations, with virtual separation of networks (VLANs) and patching of all devices and computers with latest security updates. 
\item  Responsible for ensuring the uptime of all switches across site (over 200) and other sites including, Rio Tinto Yarwun Alumina Refinery and QAL offices. 
\item  Actively take part in monthly safety meetings, and daily Lean meetings.
\item  Provide support to end users via HP Open View Service Desk 
\item  Gained useful experience in PLC 5 programming and use of SCADA systems. Obtained an understanding of Honeywell's Plantscape and Experion systems, and the use of RS Logix and OPC.
\item  Learnt invaluable safety processes and procedures for working in an industrial environment. Regular use of safety glasses, monogoggles and respirator, along with safety with hot metals, highly magnetised areas and chemicals.
    \end{list2}


    {\bf Data \#3}, Boyne Smelters Limited, Rio Tinto Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Network Administrator} \hfill {\bf December, 2007  -- January, 2008, April, 2008 -- April, 2008, September, 2008 -- October, 2008 }\\
    Details of Position:-
    \begin{list2}
        \vspace*{1mm}
\item Upgraded and maintained network infrastructure at Boyne Smelters Limited. 
\item This included installing, upgrading and configuring Cisco switches for use in production environments. 
\item Updated databases with new switch information and setting up servers. 
\item Solved critical network problems and wireless control systems issues. 
\item Arranged contractors for cable runs and expansion projects. 
\end{list2}

    {\bf Boyne Smelters Limited}, Boyne Island, Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Network Administrator} \hfill {\bf February, 2007 -- November, 2008} \\
Participated in work experience at Boyne Smelters Limited for network administration under the supervision of Brian Carroll. This includes maintaining and upgrading the site's wired and wireless network infrastructure. Assisted in Tetra radio roll out project.

    {\bf Business Information Technology Centre}, Boyne Smelters Limited, TSSHS Australia \vspace{2mm}\\\vspace{1mm}%
    {\sl Information Technology Specialist} \hfill {\bf April, 2006 -- November 2007}\\
    Details of Position:-
    \begin{list2}
        \vspace*{1mm}
\item Studied for Certificate I and III while in a work environment, following all HSE standards. 
\item Setup network and workstations for the BITS Centre. 
\item Coded login and backup scripts for the system, allowing easy login, and file redundancy. 
\end{list2}


    % Computer Skills
    \section{\mysidestyle Computer\\Experience} 

    \begin{list2}
	\item Cisco Servers:  Cisco Works, Cisco ACS, Cisco WCS
	\item Cisco Devices and Software: Switches (2940, 2950, 2960, IE 3000 / Stratix 8000, 3500, 3400 3560, 3750,4507,6509), Routers (2651,2811,2821,7206,7609)
	\item Cisco Devices and Software: Access Points (300,1131,1231,1242), WLAN Controller, ASA / ASDM, Cisco VPN Client
        \item Other Devices: Cybertec DSL and 3G routers
        \item Support and Ticketing:  OS Ticket, HP OpenView Service Desk, IPplan, VisualQSM, MediaWiki, DokuWiki, TWiki
        \item Programming: Python, C/C++, SQL (MSSQL, MySQL, sqlite), Perl, Java, Visual Basic, Linux shell scripting
        \item OS: DOS, Windows (Windows 3.1 - Windows 7 \ensuremath{\sim} Server 2008, 2003, 2000), OS X, Linux (Gentoo, Debian, Ubuntu, SUSE, RHEL), BSD (FreeBSD), Solaris
        \item Monitoring: SNMPc, Cisco Works, Zenoss, Cacti, RRDtool, Netcool CIC, IBM Tivoli, NFSen, Solarwinds Orion 
        \item Automation: RS Logix, RSMac, RS Linx, Honeywell Experion 
    \end{list2}

    % Referees
    \section{\mysidestyle Referees} 

    \begin{list2}
    \item {\sl Brian Carroll} (Superintendent IS and T Networks and Telecommunications APAC East - Rio Tinto)- 07 3625 6401
    \item {\sl Drew Ward} (Communications Engineer - Data \#3) - 04 1772 8604
    \item {\sl Brock Redgen} (Network Systems Technician - Ergon) - 04 4814 9095
    \end{list2}


\end{resume}
\end{document}
